Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 method.tex
Revised asymptotic quantity
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1116 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

In the limit of many templates, $M \gg 1$, we may neglect the cost of the forward
transform of the data and of the multiplication of the transforms.  The computational
cost will reach an optimum at some large but finite \fft\ block size
$\fftblock \gg \tmpsamps$.  In this limit, the \FD\ method costs
$\approx 2 f^0 \numtmps \lg \fftblock$ \flops.
